MSstatsPTM statistical relative quantification of post-translational modifications in global proteomics experiments

### 2021-10-26 main/MSstatsPTM_Main.tex
Meeting notes

After using the converters, the next step is peptide/protein summarization and missing value imputation. In the methods sections it was assumed that all the input data was summarized; in the implementation we need to run a specific summarization step to make this happen. For the modified run, the package summarizes features, PSMs, which include the same modification together. Features with multiple modification sites are not included with single site features and are summarized separately. For the global profiling run all unmodified features from the same protein are summarized together, up to the protein level. Additionally, the summarization includes global median normalization and normalizes between MS runs. The package uses an AFT model, as mentioned in Section \ref{sec:missing_imp}, to impute missing values, although this step is optional.

@@

>>>>

After using the converters, the next step is peptide/protein summarization and missing value imputation. In the methods sections it was assumed that all the input data was summarized; in the implementation we need to run a specific summarization step to make this happen. For the modified run, the package summarizes features, PSMs, which include the same modification together. Features with multiple modification sites are not included with single site features and are summarized separately. For the global profiling run all unmodified features from the same protein are summarized together, up to the protein level. Additionally, the summarization includes global median normalization and normalizes between MS runs. The package uses an AFT model, as mentioned in Section\todo{ \ref{sec:missing_imp}}, to impute missing values, although this step is optional.

@@

\todo{Noisy PTM measurements benefit from additional biological replicates }
